---
title: "PA1_template.Rmd"
author: "Youngkeun Yoon"
date: "2017년 4월 15일"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### What is mean total number of steps taken per day?
```{r}
data <- read.csv("activity.csv")
stepsperdate <- aggregate(steps~date, data, sum, na.rm=TRUE)
print(stepsperdate)

hist(stepsperdate$steps, breaks=17, xlab="Total Number of Steps Taken Per day")  
 

median(stepsperdate$steps)
mean(stepsperdate$steps)
```
### What is the average daily activity pattern?


```{r}

avgperinterval <- aggregate(steps~interval, data, mean, na.rm=TRUE)
plot(avgperinterval, type="l")

avgperinterval[avgperinterval$steps==max(avgperinterval$steps), ]

sum(is.na(data))
```
### Imputing missing values


```{r}
data2 <- data
narows <- is.na(data2$steps)
table(narows)

datafornarows <- tapply(data2$steps, data2$interval, mean, na.rm=TRUE, simplify=T)
data2$steps[narows] <- datafornarows[as.character(data2$interval[narows])]

nonadata <- tapply(data2$steps, data2$date, sum, simplify=T)
hist(nonadata, breaks=17, xlab="Total Number of Steps Taken Per day(imputed)")
```
Before imputation : Median(10765), Mean(10766.19)
After imputation : Median(10766.19), Mean(10766.19)
Imputation caused the median and mean to become identical. 
```{r}
median(nonadata)
mean(nonadata)
```
### Are there differences in activity patterns between weekdays and weekends?
I've coded Saturday and Sunday in Korean because of my system default language. 
```{r}


for (i in 1:nrow(data2)) {
        if (weekdays(as.Date(data2$date[i])) == "토요일" | weekdays(as.Date(data2$date[i])) == "일요일") {
                data2$daytype[i] = "weekend"
        } else {
                data2$daytype[i] = "weekday"
        }
}

        
weekenddata2 <- data2[data2$daytype=="weekend", ]
tapweekenddata2 <- aggregate(steps~interval, weekenddata2, mean, na.rm=TRUE)
weekdaydata2 <- data2[data2$daytype=="weekday", ]
tapweekdaydata2 <- aggregate(steps~interval, weekdaydata2, mean, na.rm=TRUE)
plot(tapweekenddata2, type="l")
plot(tapweekdaydata2, type="l")
```