---
title: "Assignment1"
author: "Youngkeun Yoon"
date: "2018-06-22"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Code for reading in the dataset and/or processing the data
```{r}
data <- read.csv("activity.csv")
```
##Histogram of the total number of steps taken each day
```{r}
stepsperdate <- aggregate(steps~date, data, sum, na.rm=TRUE)
head(stepsperdate)
hist(stepsperdate$steps, breaks=17, main="Total Number of Steps Taken Per day")  
```

##Mean and median number of steps taken each day
```{r}
median(stepsperdate$steps)
mean(stepsperdate$steps)
```
##Time series plot of the average number of steps taken
```{r}
timesteps <- ts(stepsperdate$steps, start=c(2012,10,1), frequency=12)
plot(timesteps)
```

##The 5-minute interval that, on average, contains the maximum number of steps
```{r}
library(plyr)
stepsperint <- ddply(data, .(interval), summarise, avgsteps=mean(steps, na.rm=T))
stepsperint[stepsperint$avgsteps==max(stepsperint$avgsteps), ]
```
##Code to describe and show a strategy for imputing missing data
```{r}
library(DMwR)
impdata <- centralImputation(data)
```
##Histogram of the total number of steps taken each day after missing values are imputed
```{r}
impstepsperdate <- aggregate(steps~date, impdata, sum, na.rm=TRUE)
head(impstepsperdate)
hist(impstepsperdate$steps, breaks=17, main="Total Number of Steps Taken Per day(imputed)")
```

        ##Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
impdata2 <- impdata
impdata2$date <- as.Date(impdata$date)
Sys.setlocale("LC_TIME", "us")
endimpdata <- impdata2[weekdays(impdata2$date)=="Saturday"|weekdays(impdata2$date)=="Sunday",]
dayimpdata <- impdata[weekdays(impdata2$date)!="Saturday"& weekdays(impdata2$date)!="Sunday",]
endstepsperint <- ddply(endimpdata, .(interval), summarise, avgsteps=mean(steps, na.rm=T))
daystepsperint <- ddply(dayimpdata, .(interval), summarise, avgsteps=mean(steps, na.rm=T))
library(ggplot2)
library(gridExtra)
gendstepsperint <- ggplot(endstepsperint) + geom_col(aes(interval, avgsteps)) + labs(title="Steps per 5 minute interval(Weekend)")
gdaystepsperint <- ggplot(daystepsperint) + geom_col(aes(interval, avgsteps)) + labs(title="Steps per 5 minute interval(Weekday)")
grid.arrange(gdaystepsperint, gendstepsperint)

```

##All of the R code needed to reproduce the results (numbers, plots, etc.) in the report
#### All R codes are included above. 

